Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-06-18 paper/sec/intro.tex
marvelous -> remarkable, rephrase

In 2022, Chakraborty, Vinodchandran, and Meel~\cite{chakraborty2022} published a streaming algorithm for the distinct elements problem which was very unexpected in the community~\cite{quanta}.
Indeed, Knuth later wrote a note on the algorithm~\cite{knuthnote}, pointing out its interesting properties and christening it the \emph{CVM} algorithm (which we use for the rest of this paper).
One striking property of the CVM algorithm is that, in contrast to every other known algorithm for the problem, it does not rely on hashing the stream elements.
Instead, the algorithm could theoretically be implemented in a setting where objects in the data stream only allow for equality comparisons.
Another property is its simplicity, which is why the authors called it ``an algorithm for the textbook''.
The algorithm is displayed in its entirety in~\cref{alg:cvm}.
% Here, $\cdot \getsr \cdot$ denotes random sampling, and $\Ber(p)$ denotes a Bernoulli distribution with parameter $p$.

>>>>

In 2022, Chakraborty, Vinodchandran, and Meel~\cite{chakraborty2022} unexpectedly published a remarkable streaming algorithm for the distinct elements problem~\cite{quanta}.
Indeed, Knuth later wrote a note on the algorithm~\cite{knuthnote}, pointing out its interesting properties and christening it the \emph{CVM} algorithm (which we use for the rest of this paper).
One striking property of the CVM algorithm is that, in contrast to every other known algorithm for the problem, it does not rely on hashing the stream elements.
Instead, the algorithm could theoretically be implemented in a setting where objects in the data stream only allow for equality comparisons.
Another property is its simplicity, which is why the authors called it ``an algorithm for the textbook''.
The algorithm is displayed in its entirety in~\cref{alg:cvm}.
% Here, $\cdot \getsr \cdot$ denotes random sampling, and $\Ber(p)$ denotes a Bernoulli distribution with parameter $p$.
